Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-05-24 paper/paper.tex
Light perf-tester refactoring, fw-install server support.

@@

\subsection{Experimental Setup}\label{sec:experimental-setup}
Evaluation of \approachshort{} was performed on server blades hosting a single Netronome Agilio LX 1x100GbE SmartNIC (NFP-6480, \SI{1.2}{\giga\hertz}).
These mid-tier servers (\emph{MidServer}) ran Ubuntu 18.04.5 LTS (4.15.0-140-generic x86\_64) on Intel Xeon Bronze 3204 CPUs ($6\times$\SI{1.9}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
We additionally use a more powerful consumer-grade machine (\emph{Collector}) for estimating host performance when offloaded to a network function, running Ubuntu 18.04.4 LTS (4.15.0-96-generic) on Intel Core i7-6700K ($4\times$\SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
Control programs were built using rustc 1.51.0.
We run \approachshort{} on an island with \num{4} MEs of the NFP-6480 for a total of \num{32} hardware threads.
This is the maximum number of MEs on a single island which is not in use by an existing P4 pipeline.
Where feasible, we test \SIlist{32;16;8}{\bit} quantised arithmetic firmware versions.
All timing and throughput measurements were repeated over \num{5000} trials.

>>>>

?? NOTE: this aggregastion step is specifically WAIT-FREE, not just lockless etc. because progress always made.

@@

\subsection{Experimental Setup}\label{sec:experimental-setup}
Evaluation of \approachshort{} was performed on server blades hosting a single Netronome Agilio LX 1x100GbE SmartNIC (NFP-6480, \SI{1.2}{\giga\hertz}).
These mid-tier servers (\emph{MidServer}) ran Ubuntu 18.04.5 LTS (4.15.0-140-generic x86\_64) on Intel Xeon Bronze 3204 CPUs ($6\times$\SI{1.9}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
We additionally use a more powerful consumer-grade machine (\emph{Collector}) for estimating host performance when offloaded to a network function, running Ubuntu 18.04.4 LTS (4.15.0-96-generic) on Intel Core i7-6700K ($4\times$\SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
Control programs were built using rustc 1.52.1.
We run \approachshort{} on an island with \num{4} MEs of the NFP-6480 for a total of \num{32} hardware threads.
This is the maximum number of MEs on a single island which is not in use by an existing P4 pipeline.
Where feasible, we test \SIlist{32;16;8}{\bit} quantised arithmetic firmware versions.
All \approachshort{} timing measurements were repeated over \num{10000} trials (preceded by \num{1000} warmup packets), from which throughput was derived.
Host throughput measures were observed over \num{10} trials of \SI{10}{\second}.
?? verify these numbers against code?
